---
title: "Data 607 Week 9 Assignment"
author: "Adriana Medina"
date: "2024-03-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
The assignment for week 9 is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame. I chose an API that retrieves the most popular article for the most recent day (24hrs).

# Load library
```{r load library}
library(httr)
library(jsonlite)
library(tidyverse)
```

# Get data
```{r request raw data}
# Construct the URL with your API key and query
api_mpurl <- "https://api.nytimes.com/svc/mostpopular/v2/viewed/1.json?api-key=AgAzv4NC9JID11LE6CNtNgiymhhf9xX3"

#fetch the raw data
rawdata <- GET(api_mpurl)

#Retrieve the status code of the HTTP response. A status code of 200 means the request was successful
rawdata$status_code
```

```{r summary of raw data}
summary(rawdata)
```

```{r extract}
#Extract the content of the raw data as a character string
extract_rawdata <- content(rawdata, as = "text")
```

# Convert from JSON-format to a df
```{r}
#Convert the JSON-formatted data to a data frame
all_data <- extract_rawdata %>% 
  fromJSON() %>% 
  as.data.frame()

colnames(all_data)
```
# Create another dataframe consisting of just the columns selected
```{r final df}
popular_articles <- all_data %>% 
  select(results.published_date,results.title, results.nytdsection)
```

__Rename column names__
```{r}
colnames(popular_articles) <- c("Published Date","Popular Articles","Section")  

glimpse(popular_articles)
```




